Embodied Neuromorphic Benchmarks

### 2015-08-16 paper/paper.tex
Tweaked working of NEF reference

Notice that we can think of this system as a three-layer neural
network, where the input and output layers are linear.  The first layer is $q$, the input state, one value for each joint.  The ``hidden'' layer
is the neurons producing activities $A$, the activity of a large number of neurons.  The output layer again has
one value per joint, and is the extra added signal to apply to the motors, $Ad$.
Given that this is a canonical example of the use of neural networks, we
expect that the majority of neuromorphic hardware is flexible enough to implement
this model.  Importantly, it functions well with spiking neuron models as 
well as non-spiking ones.  For spiking neurons, we consider $A$ to be the
instantaneous measure of the output of a neuron (i.e. whether or not it is currently outputting a spike),
filtered through a low-pass filter.  Further discussion of this sort of learning
rule and comparison to biological spiking neurons can be found in (\citealt{bekolay2013}).
This type of neural modelling forms the foundation of \cite{eliasmith2003}'s
Neural Engineering Framework, and \cite{stewart2014} have shown that spiking
and non-spiking neurons can be used in this manner to implement a wide
variety of computations.

>>>>

Notice that we can think of this system as a three-layer neural
network, where the input and output layers are linear.  The first layer is $q$, the input state, one value for each joint.  The ``hidden'' layer
is the neurons producing activities $A$, the activity of a large number of neurons.  The output layer again has
one value per joint, and is the extra added signal to apply to the motors, $Ad$.
Given that this is a canonical example of the use of neural networks, we
expect that the majority of neuromorphic hardware is flexible enough to implement
this model.  Importantly, it functions well with spiking neuron models as 
well as non-spiking ones.  For spiking neurons, we consider $A$ to be the
instantaneous measure of the output of a neuron (i.e. whether or not it is currently outputting a spike),
filtered through a low-pass filter.  Further discussion of this sort of learning
rule and comparison to biological spiking neurons can be found in (\citealt{bekolay2013}).
This type of neural modelling forms the foundation of \cite{eliasmith2003}'s
Neural Engineering Framework, which has shown that spiking
and non-spiking neurons can be used in this manner to implement a wide
variety of computations (e.g., \citealt{stewart2014}).
